Proportional multi-state multiple-cohort life table model

### 2018-04-16 MSLT/MSLTdoc.Rmd
Loop plots, not solved

@@

p_sex <- c("male", "female")
p_cause <- c("all causes", "ischemic heart disease", "ischemic stroke", "diabetes mellitus", "colon and rectum cancers", "breast cancer", "tracheal, bronchus, and lung cancer")
p_measure <- c("deaths", "ylds (years lived with disability)", "prevalence", "incidence")

@@

>>>>

#USE demography package to interpolate moratlity rates.

@@

p_sex <- c("male", "female")
p_cause <- c("all causes", "ischemic heart disease", "ischemic stroke", "diabetes mellitus", "colon and rectum cancer", "breast cancer", "tracheal, bronchus, and lung cancer")
p_measure <- c("deaths", "ylds (years lived with disability)", "prevalence", "incidence")

@@

##This works, check what is the issue with the loop. Seems that the problem was with colon and rectum cancer mispelling.

p_test <- plot_GBD(in_data1 = GBDEngland, in_data2 = GBDGL, in_sex = "male", in_cause = "colon and rectum cancer", in_measure = "deaths")
```
